Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex

\query[R1-5]{The individual variables, coupled relationships for these energy roles, and the corresponding dual variables should be explained specifically, along with the whole framework structure for equilibrium. The rationalities of the framework is not clear. At least, the current presentation is hard to follow.  }
\ans{
\green{
In the revised paper, (i) we provided a detailed description of each individual variable along with an explanation of its function in the algorithm; (ii) we re-designed the main algorithm layout; and (iii) we included a paragraph to present the targeted class of equilibria considered. Please, refer to the margin notes (R1-5) in Section III for the relative changes and additions.
}
}

\query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
\ans{In this manuscript, we want to consider the most general problem formulation of peer-to-peer markets available in the literature. Following \cite{sorin2019,lecadre2020,baroche2019b}, a linear trading cost function is introduced in the problem formulation for the purpose of product differentiation or preference prices. %Furthermore, \cite{baroche2019} also adds a trading tariff or transaction cost encoded as a 1-norm cost function. 
	Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq. \red{(8b)} in the revised manuscript) as the shadow price of bilateral trading \cite[Section 2.4]{lecadre2020}. Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}

 \query[R1-7]{The algorithm requires too many iterations, which leads to poor feasibility in real applications, especially in distributed environment. }
 \ans{
\green{The average computational time for the parallel updates of each prosumer (i.e., Algorithm 2) is $t_{\text{avg}}^{\text{pro}} = 74.5$ milliseconds; while for the DNO update (i.e., Algorithm 3), the average computational time is $t_{\text{avg}}^{\text{DNO}} = 1.13$  seconds. Hence the total running time of the proposed market-clearing algorithm (Algorithm 1) to converge to a v-GNE configuration (i.e., reach a precision of $10^{-1}$), when implemented on a real distributed system can be approximatively calculated as
\begin{align*}
\text{total running time} = \text{\# iter for convergence } \times (t_{\text{avg}}^{\text{pro}} + 	t_{\text{avg}}^{\text{DNO}}).
\end{align*}
This approximation disregards the (gather and broadcast-type) communication time which is implementation dependent.
Note that the algorithm is scalable with respect to the prosumer population size, namely, the number of iterations for convergence is not affected by the total number of prosumers in the network (see Figure \red{8}). Moreover, the computation time of the local updates is virtually also independent from the prosumer population size, for constant connectivity levels of the trading network. Therefore, the previous approximation yields running times of less than 23 minutes for our market-clearing algorithm, independently from the market size. We consider this computational-time requirement feasible for day-head or also intra-day scheduling purposes. Finally, we note that provably-convergent accelerated (inertial or over-relaxed) versions of our market-clearing mechanism can be easily devised by exploiting the algorithmic framework in based on \cite[\S~IV-B]{belgioioso2020semi} to reduce (potentially halve) the total number of iterations for convergence.
} }

@@

\query[R4-7]{ Regarding to the scalability of the algorithms, the author evaluates the convergence of the algorithm with respect to the number of agents and the connectivity, but they do not provide any information about the computational times. This is relevant to evaluate if it could be applied in a real large-scale system. }
\ans{We thank the Reviewer for raising this point. We agree that the computational time is relevant in practice and thus we have added the following statement:} %\red{particularly for the simulations with different numbers of agents}

\textit{\edit{`` The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.
		''}}

### 2022-01-13 papers/02 journal v2/journal_v14.tex
g
update 1-7

\subsection{Scalability of the algorithm}
Finally, we perform a scalability test for the proposed algorithm. Specifically, we evaluate the convergence speed, in terms of the total number of iterations required to meet a predetermined stopping criterion, when the size of the population of prosumers $N$ and the connectivity of the trading network (the number of trading links) grow. We carry out two sets of simulations.
%
For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph. Similarly, we also run ten Monte Carlo simulations for each connectivity value. We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network. \marginnote{\note{R4-7}} {\edit{The average computational time performed by each agent is 0.33 seconds per iteration.\footnote{The simulations are performed on a computer with Intel Xeon E5-2637 3.5 GHz processor and 128 GB of memory.} 
}} These results highlight that our algorithm is suitable to be applied to  large-scale systems.

>>>>

\subsection{Scalability of the algorithm}
Finally, we perform a scalability test for the proposed algorithm. Specifically, we evaluate the convergence speed, in terms of the total number of iterations required to meet a predetermined stopping criterion, when the size of the population of prosumers $N$ and the connectivity of the trading network (the number of trading links) grow. We carry out two sets of simulations.
%
For the former, we consider five different values of $N$ and a fixed connectivity level of $0.6$ and we run ten Monte Carlo simulations for each $N$, whereas in the latter, the connectivity of the trading network of $50$ prosumers varies in the range $[0.1,1]$, where connectivity $1$ means that the trading network is a complete graph. Similarly, we also run ten Monte Carlo simulations for each connectivity value. We can see from Figure \ref{fig:simE} that Algorithm~\ref{alg:alg1} suitably scales with respect to both the number of prosumers and the connectivity level of the trading network. \marginnote{\note{R4-7}} {\edit{The average computational time performed by each prosumer is 74.5 milliseconds per iteration whereas the average computational time/iteration of the DNO is 1.13 seconds on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory.} 
} These results highlight that our algorithm is suitable to be applied to  large-scale systems.
